The Skew-Normal Approximation of the Binomial Distribution

### 2011-02-08 project/paper/accuracy.tex

The first and most obvious way of judging accuracy is by visual inspection.
Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
\ref{fig:comparison-n100} in appendix \ref{app:figures} compare the binomial,
normal, and skew-normal at the small values of $p=0.05$, $p=0.1$, and $p=0.2$
for $n=25$, $n=50$, and $n=100$, respectively.

>>>>

The first and most obvious way of judging accuracy is by visual inspection.
Figures \ref{fig:comparison-n25}, \ref{fig:comparison-n50}, and
\ref{fig:comparison-n100} in appendix \ref{app:figures} compare the binomial,
normal, and skew-normal at small values of $p=0.05$, $p=0.1$, and $p=0.2$ for
each of $n=25$, $n=50$, and $n=100$, respectively.
